---
title: "Note_Vector"
author: "H24071207拾可信"
date: "2020/5/6"
output: html_document
---
# 1.Numeric Vector
### (a).Creating a Vector
```{r}
#Creat two vectors and add one vector to another.
vt1 <- c(1:5)
vt2 <- c(3:6)
vt2 <- c(vt2, vt1)
vt2
```
### (b).Simple patterned vectors
```{r}
#Use “seq()” and “rep()” to construct a vector with similar patterns.
seq(1, 5, by = 0.5)

seq(1, 10, length.out = 5)

rep(3, 12)

rep(seq(2, 10, 2), 2)

```
### (c).Creat a null or initial vector
```{r}
#If you want to assign values into a vector, you should first creat an initial vector.
```
#### version 1
```{r}
a <- c(3, 5, 9, 10)
b <- c(14, 15, 17)
V1 <- c()
V1 <- c(V1, a, b) 
V1
```
#### version 2
```{r}
b <- c(14, 15, 17)
V2 <- rep(0, 7) 
V2[1:4] <- a
V2

V2[5:7] <- b
V2
```
#### version 3
```{r}
a <- c(3, 5, 9, 10)
b <- c(14, 15, 17)
V3 <- rep(NA, 7) 
V3[1:4] <- a
V3

V3[5:7] <- b
V3
```
#### When to use “c( )” and when to use a vector with known length?
```{}
c( ): Easy to add a value into the vector; need not know the length.
rep(NA, n): With known length and the position of elements.
```
### (d).Elements in the vector
```{r}
#Use “unique( )” to return the elements that appear at least one time.
#Use “table( )” to count the number of each element from the vector.

b <- c(3, 3, 3, 3, 5, 5, 1, 2, 10, 10, 8)
unique(b)

table(b)
```
### (e).Set Operations
```{r}
B <- c(3, 1, 5, 4, 7); C <- c(23, 1, 44, 5, 3)
union(B, C)

intersect(B, C)

setdiff(B, C)

setequal(B, C)
```

```{r}
#Use “sort( )” or “order( )” to sort a vector or get the position of sorting of a vector.

#sort(x, decreasing = FALSE, . . . )
#order(. . . , na.last = TRUE, decreasing = FALSE)

a <- c(3, 4, 2, 7, 10, 23, 8, 9, 11)
sort(a)

sort(a, decreasing = TRUE)
```
### (f).Get the position of a sorted vector
```{r}
#Get the position (index) of sorting of a vector
#order(. . . , na.last = TRUE, decreasing = FALSE)

a <- c(3, 4, 2, 7, 10, 23, 8, 9, 11)
inc.order <- order(a)
dec.order <- order(a, decreasing = TRUE)
inc.order

a[inc.order]

dec.order

a[dec.order]
```
### (g).Change values in a vector
```{r}
#Change the 5th element to -3 and the 8th element to -1.

a <- c(3, 4, 2, 7, 10, 23, 8, 9, 11)
a[5] <- -3
a[8] <- -1
a
```
### (h).Deleting elements from a vector
```{r}
vt1

vt1[-2]

vt2[-c(3:6)]
```
# 2.Character vectors
### (a).Print Characters
```{r}

"Hello World!!!"

print("Hello R World!!!")
```
### (b).Split a string
```{r}
TEXT1 <- "Let's go to a game."
strsplit(TEXT1, " ")

TEXT2 <- "Hurry! We are late!"
strsplit(TEXT2, "!")
```
### (c).Lowercase and uppercase
```{r}
#toupper(): change to uppercase
#tolower(): change to lowercase

toupper(TEXT1)

tolower(TEXT2)
```
### (d).Character vectors
```{r}
#Character vector: the vector is made up of strings of characters.
#All elements of a vector must be of the same type.

colors <- c("red", "yellow", "BLUE")
more.colors <- c(colors, "green", "cyan")
more.colors

#Mix data types in a vector

z <- c("red", "green", 12)
z
```
### (e).Basic operations for character vectors
```{r}
#To take substrings, use “substr( )

colors <- c("red", "yellow", "blue")
substr(colors, 1, 3)

#To search a string from a vector, use “grep()”, which is “Global Regular Expression Print”. 
#It returns the locations of the desired patterns.

grep("y", more.colors)

grep("e", more.colors)

#To show the whole character from grep()

y.in.V <- grep("y", more.colors)
e.in.V <- grep("e", more.colors)
more.colors[y.in.V]

more.colors[e.in.V]

#“grep()” is case-sensitive(區分大小寫)

E.in.V <- grep("E", more.colors)
more.colors[E.in.V]

#To building up strings, use “paste()”.

#With space
paste(colors, "line") 

#No space
paste(colors, "line", sep = "" )

#Use ";" to seperate strings
paste("I like", colors, collapse = "; ")

```
### (f).Factors
```{r}
#factor(): factor(x = character())

colors <- c("red","yellow", "blue")
f.c <- factor(colors)
f.c

levels(f.c)

as.integer(f.c)
```
# 3.Logical Vector
### (a).Logical words
```{r}
#TRUE and FALSE are reserved words denoting logical constants in the R,
#whereas T and F are global variables whose initial values set to these.

TRUE

FALSE

T

F
```
### (b).Logical number
```{r}
c(3 < 5, 3 > 5)

c(3 <= 5, 3 >= 5)

#“==”: equal
3 == 5

#“!=”: not equal
3 != 5
```
### (c).Boolean operations
```{r}
A <- c(T, T, F, T, F)
B <- c(3, 1, 5, 4, 7)
A

B[A]

!A

B[!A]

#How many TRUE (or FALSE) in the vector?

A <- c(T, T, F, T, F)
sum(A)

sum(!A)
```
### (d).Logical vector
```{r}
#Compare the same location of elements individually.

B <- c(3, 1, 5, 4, 7); C <- c(23, 1, 44, 5, 3)
B == C

D <- c(2, 5 ,6, 10)
B == D
```
### (e).“is.” series
```{r}
#“is.XYZ()” is any comparison to the type “XYZ” of an object.
#is.null()
#is.na()
#is.nan()
#is.infinite()
#is.character()
#is.integer()
#is.numeric()

is.null(c())

c(is.na(NA), is.na(2))

x1 <- 1:5
x2 <- c(1:3, 2.2)
x3 <- colors
c(is.integer(x1), is.numeric(x1), is.double(x1))

c(is.integer(x2), is.numeric(x2), is.double(x2))

c(is.character(x3), is.numeric(x3))
```
### (f).Examine the type of a vector
```{r}
#Use “class( )” to identify the type of a vector.
a <- c(3, 4, 2, 7, 10, 23, 8, 9, 11)
b <- c("red", "yellow", "blue")
c <- c(TRUE, FALSE)
d <- f.c
c(class(a), class(b), class(c), class(d))

c(class(2), class(2.0), class(as.integer(2)))
```