---
title: "Note_ControlFlow_H24071207拾可信"
author: "H24071207拾可信"
date: "2020/5/4"
output: html_document
---

# 1.For loop 
## a lterate prsentation which can repeat the codes
## for loop can help us know the order in the lterate pocedure

Code： for (index in vector) commands
```{}
index:每執行一次迴圈，index就改變一次
vector:index可能的範圍
commands:迴圈的指令
```

```{r}
vec.X.v2 <- rep(NA, 8)
vec.X.v2[1] <- 3
for(n in 1:7){
vec.X.v2[n+1] <- 2 * vec.X.v2[n] + 3
}
vec.X.v2
vec.X.v2[2:8]

n <- 10
ans <- 1
for(j in n:1){
ans <- ans * j
}
ans
#用迴圈計算階乘
n <- 10
ans <- 1
for(j in n:1){
ans <- ans * j
}
ans
#用簡單的迴圈生成隨機變數
x0 <- 3; a <- 5; c <- 7; m <- 501
X <- rep(NA, 10)
for(j in 1:10){
x0 <- (a*x0+c) %% m
X[j] <- x0
}
X
round(X/m, 2)
```
# 2.If
## use to judge condition

Codes：if (condition) {commands when TRUE}  
       if (condition) {commands when TRUE} else {commands when FALSE}
```{}
*當變數的判斷是false時，else()提供另外一個指令
*else()的句法為選擇性，可用也可以不用
當條件只有一個時：
One condition:
if (condition) {
commands when
TRUE
} else {
commands when
FALSE
}
當條件有多個時：
Multiple conditions:
if (condition1) {
commands when condition1 is TRUE
} else if (condistion2) {
commands when condition2 is TRUE
} else {
commands when condition1 and condition2
are FALSE
}
```

```{r}
#尋找NA值所在的位置
C <- c(3, 4, NA, 12, 0.2, NA, -2)
for(i in 1:7){
  if(is.na(C[i])) print(i)
}
#尋找每個分類的數量
basket <- c("r", "b", "y", "y", "y", "r", "r", "b")
n.r <- 0; n.b <- 0; n.y <- 0
for(i in 1:length(basket)){
  if(basket[i] == "r"){
    n.r <- n.r + 1
  }else if(basket[i] == "b"){
    n.b <- n.b + 1
  }else{
    n.y <- n.y + 1
  }
}
c(n.r, n.b, n.y)
#將每個分類重新分配一個值
v.basket <- rep(NA, length(basket))
for(i in 1:length(basket)){
  if(basket[i] == "r"){
    v.basket[i] <- 1
  }else if(basket[i] == "b"){
    v.basket[i] <- 2
  }else{
    v.basket[i] <- 3
  }
}
v.basket
#用 ifelse()重新分配每個分類的值
v.basket <- ifelse(basket == "r", 1, ifelse(basket == "b", 2, 3))
v.basket
```
# 3.while loop 
## To fulfill the require of the variance, must do the calculation beforehand. Repeat by unknow reason.

Code：while (condition) statements
```{}
*當變數判斷為false時，迴圈不會有任何反應
*當變數判斷為true時，迴圈會持續執行，條件會不斷用來判斷，重複執行此過程
```

```{r}
#與for迴圈比較
for(j in 1:8){
  print(j)
}

j <- 1             #需初始化
  while(j <= 8){   #停止的條件
    print(j)       #疊代
    j <- j + 1
}
#計算丟幾次硬幣會出現正面
#0:反面;1:正面
coin <- c(0, 0, 0, 0, 0, 0, 1, 0, 1, 0, 1, 0,
1, 1, 0, 1, 1, 0, 0, 0, 1, 0, 1)
N <- c()
j <- 1
while(j <= length(coin)){
  n.fail <- 0
  while(coin[j] != 1){
    n.fail <- n.fail + 1
    j <- j + 1
  }
  N <- c(N, n.fail + 1)
  j <- j + 1
}
N
```
# 4.Break、Repeat、Next
## Break
### To stop the loop immediately, can be use in for loop and while loop

Code：if (condition) break
```{r}
Fib1 <- 1;Fib2 <- 1
Fibonacci <- c(Fib1)
for(j in 1:1000){
  if(Fib2 < 100){
    Fibonacci <- c(Fibonacci, Fib2)
    Fib1 <- Fibonacci[length(Fibonacci) - 1]
    Fib2 <- Fib1 + Fibonacci[length(Fibonacci)]
  }else{
    break
  }
}
Fibonacci

```
## Repeat
### similair to while loop ,difference between Repeat us that ut can be written in any place，and use Break to jump out the loop.

Code：repeat { statements }
```{r}
i <- 1
result <- 0
repeat{
  
  if(i>100) break
  result <- result+i
  i <- i+1
}
result
```
## Next
### when occur special occasion to jump out of the loop, can use in any loop.
```{r}
for(i in 1:10){
  if(i==5){
    next
  }
  print(i)
}
```
