---
title: "Note_Function_H24071207拾可信"
author: "H24071207拾可信"
date: "2020/5/4"
output: html_document
---

# 1.Source
## 1.finish the code 
## 2.save as XXX.R, use source to run the code
## 3.use print or cat to output the final results
```{}
*print => 顯示的字元會用引號隔開
*cat => 顯示的字元不用引號，可用"\n"將字元換行
```

```{r}
x <- c("A", "B", "C", "D")
print(x)
cat(x)
#用"\n"將字元換行
cat(x[1], "\n",
    x[2], "\n", sep = "" )
#找出完美數(使用print)
k <- 1
while(k < 100){
  fac <- c()
  for(j in 1:k){
    if((k %% j) == 0) fac <- c(fac, j)
  }
    if(k == sum(fac[-length(fac)])){
      out <- paste(paste(k, "=", sep=" "),
             paste(fac[-length(fac)], collapse = " + "),
             sep = " ")
      print(out)
  }
  k <- k+1
}
#找出完美數(使用cat)
k <- 1
while(k < 100){
  fac <- c()
  for(j in 1:k){
    if((k %% j) == 0) fac <- c(fac, j)
  }
    if(k == sum(fac[-length(fac)])){
      cat(paste(k, "=", sep=" "),
          paste(fac[-length(fac)], collapse = " + "), "\n")
  }
  k <- k+1
}
```

# 2.function(an input)
```{r}
f <- function(x){
  3*x + 2
}
f(2); f(3); f(4)
#舉例
make.percent <- function(x){
  x.percent <- round(100*x, digits = 1)
  x.show <- paste(x.percent, "%", sep = "")
  cat(x.show)
}
make.percent(c(0.8933, 0.2344, 0.0764, 0.7736))
ans <- make.percent(c(0.8933, 0.2344, 0.0764, 0.7736))
ans 
#輸出為NULL，因為函數值未貼到到ans這個變數
```
## Return
### return the parameter to the fuction after calculation
```{r}
f <- function(x){
  return(3*x + 2)
}
f(2)
f <- function(x){
  res <- 3*x + 2
}
f(2)
#因為函數算出來的值沒有回傳到函式，所以f(2)未輸出任何結果
#舉例(使用return)
make.percent <- function(x){
  x.percent <- round(100*x, digits = 1)
  x.show <- paste(x.percent, "%", sep = "")
  return(x.show)
}
make.percent(c(0.8933, 0.2344, 0.0764, 0.7736))
ans <- make.percent(c(0.8933, 0.2344, 0.0764, 0.7736))
ans
#舉例(使用invisible)
make.percent <- function(x){
x.percent <- round(100*x, digits = 1)
x.show <- paste(x.percent, "%", sep = "")
invisible(x.show)
}
make.percent(c(0.8933, 0.2344, 0.0764, 0.7736))
#使用invisible不會直接顯示計算結果，需要再命名一個新的變數來輸出結果
ans <- make.percent(c(0.8933, 0.2344, 0.0764, 0.7736))
ans
```
## Fuction name
### View as an object
```{r}
objA <- function(x){
  return(2*x)
}
objA #輸出為一個函數
objA <- objA(4)
objA #輸出為一個向量
```
# 3.function(multiple input)
```{r}
f <- function(x, y){
  x^2 + y^2
}
f(2, 2); f(2, 3); f(2, 4)
#舉例
make.percent <- function(x, x.digits){
  x.percent <- round(100*x, digits = x.digits)
  x.show <- paste(x.percent, "%", sep = "")
  return(x.show)
}
make.percent(c(0.8933, 0.2344, 0.0764, 0.7736), 0)
make.percent(c(0.8933, 0.2344, 0.0764, 0.7736), 1)
make.percent(c(0.8933, 0.2344, 0.0764, 0.7736), 2)
#參數設定一個預設值
make.percent <- function(x, x.digits = 0){
  x.percent <- round(100*x, digits = x.digits)
  x.show <- paste(x.percent, "%", sep = "")
  return(x.show)
}
make.percent(c(0.8933, 0.2344, 0.0764, 0.7736))
make.percent(c(0.8933, 0.2344, 0.0764, 0.7736), 0)
```
# 4.use function or return to output multiple results
## list：a vector that can save different type of elements
```{r}
X <- list(a = 3, b = c(1,2,3,4,5), c = c("A", "B"))
X
```
### use $ or [[ ]] to extract the elements in list
$：element name 
[[ ]]：element name or position
```{r}
X <- list(a = 3, b = c(1,2,3,4,5), c = c("A", "B"))
X$a
X[[2]]
X[["c"]]
```
build a list
```{r}
create <- list()
length(create)
length(create) <- 2
create[[1]] <- seq(1,5,2)
create
create$plus <- seq(1,5,2)+3 #新命名的物件會放在list的最後面
create
create[[2]]
create[[3]]
names(create)
length(create)        #list的長度因為新增一個名為plus的物件所以+1
#舉例
perfect.number <- function(a, b){
  k <- a
  res <- c()
  ans <- list()
  while(k < b){
    fac <- c()
    for(j in 1:k){
      if((k %% j) == 0) fac <- c(fac, j)
    }
      if(k == sum(fac[-length(fac)])) {
      res <- c(res, k)
      ans[[paste(k)]] <- fac[-length(fac)]
    }
      k <- k+1
  }
  ans$number <- res
  return(ans)
}
Ans <- perfect.number(1, 100)
Ans
Ans[["28"]]
```