---
title: "Note_Introduction_H24071207拾可信"
author: "H24071207拾可信"
date: "2020/5/6"
output: html_document
---

# 1.Introduction to Calculation
### (a).Calculator
```{r}
5 + 3

5 * 3

5 / 3

5 ^ 3

5 %% 3

5 %/% 3

```

### (b).Sequenece
```{r}
1:10

seq(1, 10, 2)

seq(1, 10, length.out = 6)
```

### (c).Basic features in R
```{r}
#Calculating with R
#Named storage: assign a name to a value.

a <- 3 ^ 5
b = 3 ^ 5
a

b
```

### (d).Calculation by the set values
```{r}
a <- 1000
b <- 4
a * b - a
```

### (e).Special values in R
```{r}
NA

NaN #ex: 0/0

Inf #ex: 2/0

-Inf #ex: -2/0

pi

1e-3
```

### (f).Name an objuect
```{}
#Avoid the following words:
#break; else; FALSE; F; TRUE; F; for; function; if; Inf; NA; NaN; next;repeat; return; while;

#Name a meaningful object by “.” or "_".
#score1, score2 
#score.John, score.Jack
```

### (g).More on calculation
```{r}
#Absolute value: |x|
abs(-2)

#Exponential & logarithm: exp(x), log(x)
exp(10); log(2); log2(2); log(10); log10(10);


```

### (h).Other functions
```{r}
#“ˆ” or "**" means the degree of the power.
2 ** 3; 2^3;2^0.5; sqrt(2);
```

### (i).Approximated values
```{r}
round(125.78253) 

round(125.78253, digits = 3)
#決定小是位數
round(125.78253, digits = -2);

round(83524587, digits = -3); round(83524587, digits = -5);

signif(125.78253, digits = 2);
#四捨五入
signif(83524587, digits = 3); signif(83524587, digits = 5);


floor(125.78253);
#無條件捨去
ceiling(125.78253);
#無條件進位
trunc(125.78253); 
# extract the integer part
```

### (j).Descriptive statistics
```{r}

x <- 1:25
mean(x)

var(x)

median(x)

quantile(x, c(0.1, 0.5, 0.7))

x <- c(1:25, NA)
summary(x)
```

### (k).R is case-sensitive
```{r}

#If type MEAN()
x <- c(1:25)
#MEAN(x)
## Error in MEAN(x): could not find function "MEAN"

#Now, set:
MEAN <- mean
MEAN(x)
```

### (l).Objects in your workspace
```{r}
objects()

ls()
#If you want to delete some objects, you can type:
rm(x, y)
#Now, see again what you have in your workspace.
objects()

#You can see your objects on your topright corner also.
```

# 2.Introduction to Vectors
### (a).Vectors
```{r}
vt1 <- c(2:4)
vt2 <- c(3:6)
vt2 <- c(vt2, vt1)
vt2

vt2 <- c(vt2, vt1)
vt2
```

### (b).Some common functions to vectors
```{r}
length(vt1) 

length(vt2)

#Extracting elements from vectors, use [ ] to select the locations in thecvector.
# ## Note that the count is different from C and python.

vt1[3]

vt2[c(3,5,7)]

#We can select some elements of the vector as follows:

vt1

vt1[-2]

vt2[-c(3:6)]
```

### (c).Vector arithmetic
```{r}
x <- c(3, 6, 9)
x * 3

x - 3

x ^ 3

y1 <- c(3, 2); y2 <- c(3, 2, 4);
#longer object length is not a multiple of shorter object length

x^y1

x^y2

#When the vectors are different lengths, the shorter one is extended by recycling.

c(1, 1, 2, 2, 3, 3, 4, 4, 5, 5,
6, 6, 7, 7, 8, 8, 9, 9, 10, 10) %% 2:3

#Recycling: rep(x, ntimes)

c(1, 1, 2, 2, 3, 3, 4, 4, 5, 5,
6, 6, 7, 7, 8, 8, 9, 9, 10, 10) %% rep(2:3, 10)

```

### (d).Simple patterned vectors
```{r}
#Use “seq()” and “rep()” to construct a vector with similar patterns.

rep(3, 12)

rep(seq(2, 10, 2), 2)

rep(c(1, 4), c(3, 2))

rep(seq(2, 10, 2), rep(3, 5))
```

### (e).Assign values into a vector
```{r}
Xvector <- rep(NA, 6)
Xvector[3] <- 12
Xvector[c(4:6)] <- rep(1, 3)
Xvector

#To delete NA
Xvector[-(1:2)]
## [1] 12 1 1 1
Xvector <- Xvector[-(1:2)]
Xvector
```

# 3.Introduction to Matrix
### (a).Construct a matrix by row
```{r}
a <- 1:5; b <- 6:10;
c <- 11:15; d <- 16:20;

M1 <- rbind(a, b, c, d)
M1
```

### (b).Construct a matrix by column
```{r}
M2 <- cbind(a, b, c, d)
M2

```

### (c).Constrict a matrix by a long vector
```{r}
X <- 1:20
matrix(X, nrow = 4, ncol = 5)

matrix(X, nrow = 5, ncol = 4)

matrix(X, nrow = 4, ncol = 5, byrow = TRUE)

matrix(X, nrow = 5, ncol = 4, byrow = TRUE)
```

### (d).Features for a matrix
```{r}
dim(M1) #Show the diamension of matrix

colnames(M1); 
rownames(M1);

colnames(M1) <- c("V1", "V2", "V3", "V4", "V5") #Assign column names
```

### (e).Extract elements from a matrix
```{r}
#Use “[ ]” to extract elements from a matrix, 

M1[2, 4];
#M1[5, 5]; #Out of bond

M1[c(2, 4), 3]; 

M1[c(2, 4), c(3, 5)];
M1
```

### (f).Extract a row or a column from a matrix
```{r}
M1[, 4]; 
#M1[5, ]; #out of bond

M1[c(2, 4), ];
M1[, c(3, 5)]
```

### (i).Extract elements from a matrix
```{r}
M2

M2[5]
M2[13]
```