---
title: "Note_Apply_H24071207拾可信"
author: "H24071207拾可信"
date: "2020/5/5"
output: html_document
---

# 1.Apply
## Use function in sipecific data x，By using margin to assign function process by column or row
```{}
句法：apply(x,margin,function...)
x：矩陣或資料框
margin：以矩陣為例，1代表矩陣的列，2代表矩陣的行
function：想執行的函數
```

```{r}
A <- matrix(rnorm(100), 10, 10)
apply(A, 1, sum)
rowSums(A)
apply(A, 2, sum)
colSums(A)
#計算列的總和
row.col.sum <- function(X, margin = 1){
  size <- dim(X)
  if(margin == 1){
    res <- c()
    for(j in 1:size[1]){
      res <- c(res, sum(X[j,]))
    }
  }else if(margin == 2){
    res <- c()
    for(j in 1:size[2]){
      res <- c(res, sum(X[,j]))
    }
  }else{
    stop("margin should be either 1 or 2.")
  }
  return(res)
}
#比較三種不同方法所花費的時間
#install.packages("rbenchmark")
library(rbenchmark)
benchmark(replications=rep(1000, 1),
          apply(A, 1, sum), rowSums(A), row.col.sum(A, 1),
          columns=c('test', 'elapsed', 'relative'))
#當資料有NA值時
B <- matrix(sample(1:100, 15), 5, 3)
B[1, 2] <- NA
B[3, 1] <- NA
B <- data.frame(B)
colnames(B) <- c("factor 1", "factor 2", "factor 3")
apply(B, 2, mean)
#移除NA值
apply(B, 2, mean, na.rm = TRUE)
```
# 2.lapply
## similair to apply，use function to data x，though lapply can not process by specific row or column, x usually us one diamansion vector
```{}
句法：lapply(x,function,...)
x：向量或資料框
function：想執行的函數
```

```{r}
C <- list(a = 1:10, beta = exp(-3:3))
#如果在這邊用apply，會出現Error，因為dim(X)必須是正整數
lapply(C, mean)
#用lapply輸出圖表
par(mfrow = c(1, 2))
lapply(C, hist)
```
# 3.sapply
## similair to lapply，use function to data x,difference  between lapply is that sapply will respond a vector, not a list
## sapply will respond sequense and vector with same lengthen
```{}
句法：sapply(x,function,...,simplify=TRUE)
x：向量、list或資料框
function：想執行的函數
simplify：將回傳的list簡單化(預設為TRUE)
```

```{r}
sapply(C, summary)
sapply(C, summary, simplify = FALSE)
lapply(C, summary)
```

```{r}
#資料為list，sapply回傳也會是list
D <- list(a = sample(1:10, 10, replace = TRUE),
b = sample(1:5, 20, replace = TRUE))
sapply(D, unique)
#和lapply比較
lapply(D, unique)
#sapply也能回傳table
sapply(D, table)
```